The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-01 exp-resurgence.tex
Drop old draft passages about `reg-sing-volterra` on coverings

\begin{todo}Move before calculation of Laplace transform of convolution, write more if needed, and also make sure it's actually correct. The old text below has mistakes.\end{todo}
\begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
\begin{todo}[actually need $\Omega_0$ in lemma]\end{todo}
\begin{lemma}
If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \begin{todo}[no; revise]\end{todo} under the convolution product $\ast_{\zeta, \alpha}$.
\textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
\end{lemma}
\begin{proof}
Suppose $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. The convolution integral
\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,|d\zeta| \]
can then always be evaluated along the path $\zeta = (1-t)\,\alpha + t\,\zeta(a)$ parameterized by $t \in (0, 1)$.

For any $\phi, \psi \in \singexp{\sigma}{\Lambda}(\Omega_\alpha)$, we have
\begin{align*}
\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & = \left| \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta \right| \\
& \le \int_{\zeta = \alpha}^a |\psi|\,|\mathsf{R}^*\phi|\,|d\zeta| \\
& \le \int_{\zeta = \alpha}^a \Big( |\zeta - \alpha|^\sigma e^{\Lambda|\zeta - \alpha|}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( |\zeta(a) - \zeta|^\sigma e^{\Lambda|\zeta(a) - \zeta|}\,\|\phi\|_{\sigma, \Lambda} \Big)\,|d\zeta|.
\end{align*}
Using the shorthand $\delta \defeq |\zeta(a) - \alpha|$, we compute
\begin{align*}
\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & \le \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,dt \\
& = \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,d\zeta
\end{align*}
\begin{todo}[\ldots]\end{todo}
\end{proof}
\begin{verify}
\begin{proof}
    \begin{align*}
    |\series{\phi}\ast\series{\psi}|&=\left|\int_0^\zeta\series{\phi}(\zeta-\zeta')\series{\psi}(\zeta')\, d\zeta'\right|\\
        &\le \int_0^\zeta |\series{\phi}(\zeta-\zeta')||\series{\psi}(\zeta')|\, d\zeta'\\
        &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')|-\zeta+\zeta+\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta+\zeta'|}\, d\zeta'\\
        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')(|\zeta|+|-\zeta+\zeta'|)^{\sigma}e^{\Lambda(|\zeta|+|-\zeta+\zeta'|)}\, d\zeta'\\
        &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\series{\psi}||_{\sigma,\Lambda} ||\series{\phi}||_{\sigma,\Lambda}. 
    \end{align*}
\end{proof}
\end{verify}
\begin{corollary}
For any $\sigma > -1$ and $\Lambda > 0$, the Laplace transform 
\[ \laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\Omega_\alpha) \to \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
is a $\C$-algebra isomomorphism, with inverse defined in Proposition~\ref{prop:inverse_laplace_analytic}. 
\end{corollary}\end{old}
%
\subsubsection*{The Borel transform as algebra isomomrphism}
%
The Borel transform $\borel_\zeta$ is defined on the space of formal power series $z^{-1}\C\llbracket z^{-1}\rrbracket$, which is a $\C$-algebra, with product given by the Cauchy product of formal power series. In addition, introducing the formal unit $\delta$, the Borel transform can be extended to $\C\llbracket z^{-1}\rrbracket$ (including constants), as $\borel_\zeta(1)=:\delta$. Therefore, the Borel transform is a $\C$-linear map
 \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\,.\] 
In fact, since $\borel_\zeta$ is defined as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity. As a result, we find that the Borel transform is a $\C$-linear invertible map whose inverse is the formal Laplace transform.

@@

To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$. On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$. Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
\begin{brainstorm}
\item \begin{todo}[Find right phrasing]\end{todo} Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes. The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
\end{brainstorm}

\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[ietcoast!33] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[ietcoast!33!black] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
  \node[ietcoast!33!black] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill[ietcoast!33!black] \p circle (0.7mm);
  }
\end{tikzpicture}
\captionof{figure}{The domain $\Upsilon$ at $\zeta=\alpha$.}\label{fig:domain_Upsilon}
\end{center}
For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$. This operator is bounderd, so its kernel is closed.
\end{proof}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. Noting that \begin{draft}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{draft},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray. This, as discussed above, proves the desired result.
\end{proof}
\color{black}

@@

\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

>>>>

\subsubsection*{The Borel transform as algebra isomomrphism}
The Borel transform $\borel_\zeta$ is defined on the space of formal power series $z^{-1}\C\llbracket z^{-1}\rrbracket$, which is a $\C$-algebra, with product given by the Cauchy product of formal power series. In addition, introducing the formal unit $\delta$, the Borel transform can be extended to $\C\llbracket z^{-1}\rrbracket$ (including constants), as $\borel_\zeta(1)=:\delta$. Therefore, the Borel transform is a $\C$-linear map
 \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\,.\] 
In fact, since $\borel_\zeta$ is defined as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity. As a result, we find that the Borel transform is a $\C$-linear invertible map whose inverse is the formal Laplace transform.

@@

To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$. On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$. Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
\begin{lemma}\label{lem:shifted_holo_closed}
Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$. Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
\begin{center}
\begin{tikzpicture}
  \newcommand{\spill}{4}
  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
    (-\spill, -\spill) (\spill, \spill)
    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
  \fill[ietcoast!33] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
  \fill[ietcoast!33!black] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
  \node[ietcoast!33!black] at (-190:0.85) {$\Upsilon_\Delta$};
  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
    \fill[ietcoast!33!black] \p circle (0.7mm);
  }
\end{tikzpicture}
\captionof{figure}{The domain $\Upsilon$ at $\zeta=\alpha$.}\label{fig:domain_Upsilon}
\end{center}
For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
\end{lemma}
\begin{proof}
Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$. The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap. Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
is bounded. A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$. This operator is bounderd, so its kernel is closed.
\end{proof}

@@

Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$. This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
\begin{align*}
|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
& \lesssim \Delta^{-1}
\end{align*}
along any ray. This, as discussed above, proves the desired result.
\end{proof}
\color{black}

@@
